\mireval{}

### 2014-05-08 paper/paper.tex
Minor edits

@@

\begin{table}[htb]
\label{tab:nexamples}
  \centering
\begin{tabularx}{\columnwidth}{l c c c}
\toprule
Task & Algorithms & Examples & Scores\\
\midrule
Beat Detection & 20 & 679 & 13580\\
Segmentation & 8 & 1397 & 11176 \\
Onset Detection & 11 & 85 & 935 \\
Chord Estimation & 12 & 217 & 2604 \\
Melody & 1 & 20 & 20 \\
Pattern Discovery & 4 & 5 & 20 \\
\bottomrule
\end{tabularx}
\end{table}

@@

\begin{table*}[htb]
\label{tab:comparison}
  \centering
\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
 \multicolumn{5}{ c }{Chord Estimation} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabularx}
\end{table*}

@@

In the computation of the F-measure, precision and recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
In MIREX, this assignment is done in a greedy fashion, however in \mireval{} we use an optimal matching strategy.
This is accomplished by computing a maximum bipartite matching between the estimated events and the reference events (subject to the window constraint) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.
This explains the observed discrepancy between \mireval{} and MIREX for each of these metrics.
In all cases where the metric differs, \mireval{} reports a higher score, indicating that the greedy matching strategy was suboptimal.

@@

The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
The Beat Evaluation Toolbox uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.

>>>>

% Add table captions
% Add conclusion
% Fill in missing segmentation explanations

@@

\begin{table}[htb]
  \centering
\begin{tabularx}{\columnwidth}{l r r r}
\toprule
Task & Algorithms & Examples & Scores\\
\midrule
Beat Detection & 20 & 679 & 13580\\
Segmentation & 8 & 1397 & 11176 \\
Onset Detection & 11 & 85 & 935 \\
Chord Estimation & 12 & 217 & 2604 \\
Melody & 1 & 20 & 20 \\
Pattern Discovery & 4 & 5 & 20 \\
\bottomrule
\end{tabularx}
 \label{tab:nexamples}
\end{table}

@@

\begin{table*}[htb]
  \centering
\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
 \multicolumn{5}{ c }{Chord Estimation} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.163\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabularx}
\label{tab:comparison}
\end{table*}

@@

In the computation of the F-measure, precision and recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
No estimated event is counted as a hit for more than one reference event, and vice versa.
In MIREX, this assignment is done in a greedy fashion, however in \mireval{} we use an optimal matching strategy.
This is accomplished by computing a maximum bipartite matching between the estimated events and the reference events (subject to the window constraint) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.
This explains the observed discrepancy between \mireval{} and MIREX for each of these metrics.
In all cases where the metric differs, \mireval{} reports a higher score, indicating that the greedy matching strategy was suboptimal.

@@

The Information Gain metric \cite{davies2009evaluation} involves the computation a histogram of the per-beat errors.
The Beat Evaluation Toolbox (and therefore MIREX) uses a non-uniform histogram binning where the first, second and last bins are smaller than the rest of the bins while \mireval{} uses a standard uniformly-binned histogram.
As a result, the Information Gain score reported by \mireval{} differs substantially from that reported by MIREX.
